---
title: "Open vs. Closed Innovation"
author: "Oliver Bott"
date: "Wednesday, December 03, 2014"
output: ioslides_presentation
---

```{r, echo=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
# Set working directory
setwd('C:/Users/a6p/Desktop/Uni 2014/E1161 - Collaborative Research/GitHub Clone/Final_Project/Presentation/')

library(RCurl)
library(ggmap)
library(maptools)
library(dplyr)
library(reshape2)
library(maps)
library(stargazer)
library(rCharts)

# Load .csv from GitHub repository
options(RCurlOptions = list(cainfo = system.file("CurlSSL", "cacert.pem", package = "RCurl")))

# Create dynamic link to Dataset.csv created through the Data_Gathering.R
x <- getURL('https://raw.githubusercontent.com/oliverbott/Final_Project/master/Data/Dataset.csv')
dataset <- read.csv(text = x)
dataset$X <- NULL
colnames(dataset) <- c("METRO_ID" , "Patents" , "GDP" , "Population", "Greenspace", "Employment" , "Pollution" , "lon" , "lat" , "Followers" , "1" , "10" , "20" , "30" , "40" , "50" , "60" , "70" , "80" , "90" , "100" , "US" , "DE" , "FR" , "JP" , "hifol")
```

```{r, echo=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
# This code is needed to use the rCharts

## utility function to add required assets such as CSS and JS libraries
add_lib_assets <- function(lib, cdn = F, css = NULL) {
    assets = get_assets(get_lib(lib), cdn = cdn)
    if (!is.null(css)) {
        assets$css = c(assets$css, css)
    }
    styles <- lapply(assets$css, function(style) {
        sprintf("<link rel='stylesheet' href=%s>", style)
    })

    scripts <- lapply(assets$jshead, function(script) {
        sprintf("<script type='text/javascript' src=%s></script>", script)
    })
    cat(paste(c(styles, scripts), collapse = "\n"))
}

# get assets from online repositories
add_lib_assets("NVD3", cdn = TRUE, css = "http://rawgithub.com/ramnathv/rCharts/master/inst/libraries/nvd3/css/rNVD3.css")
```

## What are we doing here?

How many groups in this class have done something:

- interesting
- creative
- **innovative**

Why is innovation important?

- economic growth
- sustainability
- education

How is innovation measured?

- For the last few decades, measured through **patents**

## Why Patents

Patents were used because:
- defined moment and place in time (registration)
- a legal claim of a new idea
- same 'innovation' can't be claimed twice

## But:

Intuitively, seems many innovations are taking place which aren't being patented

## Open Innovation

Focused on software innovation
Used Github API
Used **follower** numbers

## Goal

Wanted to see if there is a relationship between classical innovation, and open innovation

## Data

We pulled and cleaned follower data, patent data, and some other variables for 120 cities to see if we can find a relationship between follower and patent data, and these and 'explanatory' variables

## Finding Innovation

This is an alternative interactive plot.

```{r, echo=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

fol <- dataset

fol$X <- NULL
fol$Patents <- NULL
fol$GDP <- NULL
fol$Population <- NULL
fol$Pollution <- NULL
fol$Greenspace <- NULL
fol$Employment <- NULL
fol$lon <- NULL
fol$lat <- NULL
fol$Followers <- NULL
fol$hifol <- NULL

# Rename variables for melting
colnames(fol) <- c("METRO_ID" , "1" , "10" , "20" , "30", "40", "50", 
                       "60", "70", "80", "90", "100" , "US" , "DE" , "FR" , "JP")
  # 1 means 1-9 followers, 10 equals 10-19 followers etc.

new <- fol
new_2 <- reshape(new, 
                 varying = c("US", "DE", "FR", "JP"), 
                 v.names = "value",
                 timevar = "Country", 
                 times = c("US", "DE", "FR", "JP"), 
                 new.row.names = 1:1000,
                 direction = "long")

new_2 <- subset(new_2, value>0)
new_2$id <- NULL 
new_2$value <- NULL
new_2$Country <- as.factor(new_2$Country)
x_2 <- split(new_2, new_2$Country)
x_3 <- lapply(x_2, function (x) sapply(x, mean))
x_3 <- data.frame(x_3)
x_3 <- na.omit(x_3)

df <- reshape(x_3, 
                 varying = c("US", "DE", "FR", "JP"), 
                 v.names = "value",
                 timevar = "Country", 
                 times = c("US", "DE", "FR", "JP"), 
                 new.row.names = 1:1000,
                 direction = "long")
variable <- c(1,10,20,30,40,50,60,70,80,90,100, 
              1,10,20,30,40,50,60,70,80,90,100,
              1,10,20,30,40,50,60,70,80,90,100,
              1,10,20,30,40,50,60,70,80,90,100)
df <- data.frame(df, variable)
df$id <- NULL 
df$variable <- as.factor(df$variable)

n1 <- nPlot(value ~ variable, group = "Country", data = df, type = "multiBarChart")
n1$print("chart3")
```

## City overview - Europe

```{r, echo=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}


# Map of European cities
europe.center <- geocode("Europe")
eumap <- qmap(c(lon=europe.center$lon, lat=europe.center$lat), source = 'google', color="bw", zoom=4)
eumap + geom_point(aes(x=lon, y=lat), data=dataset) + 
        geom_point(aes(x = lon, y = lat, color=hifol, size=20), data = dataset) + 
        scale_colour_gradient(low="#2c7fb8", high="#f03b20") + guides(size=FALSE)
#guide legend = false or something
# + guides(size=FALSE)
```

## City overview - Japan

```{r, echo=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
# Map of Japanese cities
japan.center <- geocode("Japan")
japanmap <- qmap(c(lon=japan.center$lon, lat=japan.center$lat), source='google', color="bw", zoom=5)
japanmap + geom_point(aes(x=lon, y=lat), data=dataset) + 
        geom_point(aes(x = lon, y = lat, color=hifol, size=20), data = dataset) + 
        scale_colour_gradient(low="#2c7fb8", high="#f03b20") + guides(size=FALSE)
```

## City overview - America

```{r, echo=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
# Map of American cities
america.center <- geocode("Cuba")
americamap <- qmap(c(lon=america.center$lon, lat=america.center$lat), source='google', color="bw", zoom=3)
americamap + geom_point(aes(x=lon, y=lat), data=dataset) + 
        geom_point(aes(x = lon, y = lat, color=hifol, size=20), data = dataset) + 
        scale_colour_gradient(low="#2c7fb8", high="#f03b20") + guides(size=FALSE)
```

## Correlation?

- Maybe add correlation matrix here. Use it?

## Nerd Slide: Our Model

$logP_{i} = {\beta}_0 +{\beta}_1 logF_{i} + {\beta}_2 logControls_{i} +{\epsilon}_{i}$


```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
# Regression table with stargazer

# For log delete 0 follower categories: new datasetlog
datasetlog <- dataset
#datasetlog[-c(45, 59, 62, 63, 73, 81, 90, 116, 121), ]
datasetlog <- datasetlog[-c(45, 59, 62, 63, 73, 81, 90, 116, 121), ]

# Create country interaction
datasetlog$USfol <- datasetlog$hifol*datasetlog$US
datasetlog$DEfol <- datasetlog$hifol*datasetlog$DE
datasetlog$FRfol <- datasetlog$hifol*datasetlog$FR
datasetlog$JPfol <- datasetlog$hifol*datasetlog$JP

P1 <- lm(log(Patents) ~ log(hifol), data = datasetlog)
P2 <- lm(log(Patents) ~ log(hifol) + log(GDP) + log(Population) + 
           log(Greenspace) + log(Employment) + log(Pollution), data = datasetlog)
P3 <- lm(log(Patents) ~ log(hifol) + log(GDP) + log(Population) + 
           log(Greenspace) + log(Employment) + log(Pollution) + USfol + DEfol + FRfol + JPfol, data = datasetlog)

labelsP <- c('Over 20 Followers', 'GDP', 'Population', 'Greenspace', 'Employment', 'Pollution', 'US' , 'DE' , 'FR' , 'JP', '(Intercept)')
```

## Regression output

```{r, echo=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
stargazer::stargazer(P1, P2, P3, covariate.labels = labelsP,
  title = 'Regression Estimates of Patent Activity',
  digits = 2, type ='html', single.row=TRUE)
```


## Alternative scatterplot

```{r, echo=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
countryset <- data.frame (id=1:132)

countryset$METRO_ID <- c('Vienna', 'Graz', 'Linz', 'Brussels', 'Antwerp', 'Ghent', 'Liege', 'Berlin', 'Hamburg', 'Munich', 'Cologne', 'Frankfurt', 'Essen', 'Stuttgart', 'Leipzig', 'Dresden', 'Dortmund', 'Dusseldorf', 'Bremen', 'Hanover', 'Bochum', 'Freiburg', 'Augsburg', 'Bonn', 'Karlsruhe', 'Duisburg', 'Mannheim', 'Aachen', 'Copenhagen', 'Tallinn', 'Madrid', 'Barcelona', 'Valencia', 'Seville', 'Zaragoza', 'Malaga', 'Palmas', 'Bilbao', 'Helsinki', 'Paris', 'Lyon', 'Toulouse', 'Strasbourg', 'Bordeaux', 'Nantes', 'Lille', 'Montpellier', 'Rennes', 'Grenoble', 'Toulon', 'Marseille', 'Nice', 'Rouen', 'Rome', 'Naples', 'Turin', 'Palermo', 'Genova', 'Florence', 'Bologna', 'Catania', 'Venice', 'Mito', 'Tokyo', 'Kofu', 'Nagoya', 'Numazu', 'Osaka', 'Okayama', 'Kurashiki', 'Fukuyama', 'Hiroshima', 'Takamatsu', 'Monterrey', 'Irapuato', 'Hague', 'Amsterdam', 'Rotterdam', 'Utrecht', 'Oslo', 'Lisbon', 'Porto', 'Stockholm', 'Gothenburg', 'Malmo', 'Seattle', 'Portland', 'Minneapolis', 'Milwaukee', 'Madison', 'Buffalo', 'Albany', 'Detroit', 'Boston', 'Chicago', 'Providence', 'Toledo', 'Cleveland', 'Omaha', 'Akron', 'Pittsburgh', 'Harrisburg', 'Philadelphia', 'Columbus', 'Denver', 'Indianapolis', 'Dayton', 'Baltimore', 'Cincinnati', 'Washington', 'Louisville',  'Wichita', 'Richmond', 'Fresno', 'Nashville', 'Tulsa', 'Raleigh', 'Charlotte', 'Albuquerque', 'Memphis', 'Columbia', 'Atlanta', 'Phoenix',  'Dallas', 'Charleston', 'Tucson', 'Austin', 'Jacksonville', 'Houston', 'Orlando', 'Tampa', 'Miami')
countryset$id <- NULL

countryset$Country <- c('Austria', 'Austria', 'Austria', 'Belgium', 'Belgium', 'Belgium', 'Belgium', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Denmark', 'Estonia', 'Spain', 'Spain', 'Spain', 'Spain', 'Spain', 'Spain', 'Spain', 'Spain', 'Finland', 'France', 'France', 'France', 'France', 'France', 'France', 'France', 'France', 'France', 'France', 'France', 'France', 'France', 'France', 'Italy', 'Italy', 'Italy', 'Italy', 'Italy', 'Italy', 'Italy', 'Italy', 'Italy', 'Japan', 'Japan', 'Japan', 'Japan', 'Japan', 'Japan', 'Japan', 'Japan', 'Japan', 'Japan', 'Japan', 'Mexico', 'Mexico', 'Netherlands', 'Netherlands', 'Netherlands', 'Netherlands', 'Norway', 'Portugal', 'Portugal', 'Sweden', 'Sweden', 'Sweden', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States',  'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States',  'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States')

datasetscat <- merge(dataset , countryset , by=c("METRO_ID")) 


n2 <- nPlot(Patents ~ hifol, data = datasetscat, type = "scatterChart", 
    group = "Country")
n2$xAxis(axisLabel = "Sepal.Width")  # add x axis label
n2$yAxis(axisLabel = "Sepal.Length")
n2$print("nvd3Scatter")
```

## Implications

**Preliminarily** using open data is a potentially innovative way of measuring innovation (see what we did there?)

Could be used in the future for 