---
title: "Website_Test"
author: "Oliver Bott"
date: "Monday, December 08, 2014"
output: html_document
---

---
title: "Website"
author: "Oliver Bott and Benjamin Snow"
date: "Monday, December 08, 2014"
output: html_document
---


```{r, echo=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
# Set working directory

library(RCurl)
library(ggmap)
library(maptools)
library(dplyr)
library(reshape2)
library(maps)
library(stargazer)
library(rCharts)

# Load .csv from GitHub repository
options(RCurlOptions = list(cainfo = system.file("CurlSSL", "cacert.pem", package = "RCurl")))

# Create dynamic link to Dataset.csv created through the Data_Gathering.R
x <- getURL('https://raw.githubusercontent.com/oliverbott/Final_Project/master/Data/Dataset.csv')
dataset <- read.csv(text = x)
dataset$X <- NULL
colnames(dataset) <- c("METRO_ID" , "Patents" , "GDP" , "Population", "Greenspace", "Employment" , "Pollution" , "lon" , "lat" , "Followers" , "1" , "10" , "20" , "30" , "40" , "50" , "60" , "70" , "80" , "90" , "100" , "US" , "DE" , "FR" , "JP" , "hifol")
```

## What are we doing here?

How many groups in this class have done something:

- Interesting?

- Creative?


How many groups in this class have done something:

- Interesting?

- Creative?

- **Innovative**?

Why should we be interested in innovation?

- Economic growth

- Sustainability



## Measuring innovation

Innovation has mostly been measured in **patents**, but why?

- Defined moment and place in time

- Legal claim of a new idea, vital for commercialization

- Same *innovation* cannot be claimed twice

- Shortcomings?


**Research question:**

**To what extent can open innovation network data add to the measurement of innovation performance?**


## Methodology

We look at relationship between open and closed innovation

Comparison of **GitHub** API users' follower numbers to **OECD** patent data in **132** cities in **16** countries


Research design has some limitations:

- Timing discrepancies

- Exclusion of some major tech-cities


Diffusion of GitHub - underestimating effect?

## City overview - Europe

```{r, echo=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}


# Map of European cities
europe.center <- geocode("Europe")
eumap <- qmap(c(lon=europe.center$lon, lat=europe.center$lat), source = 'google', color="bw", zoom=4)
eumap + geom_point(aes(x=lon, y=lat), data=dataset) + 
        geom_point(aes(x = lon, y = lat, color=hifol, size=20), data = dataset) + 
        scale_colour_gradient(low="#2c7fb8", high="#f03b20") + guides(size=FALSE)
#guide legend = false or something
# + guides(size=FALSE)
```

```{r, echo=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
countryset <- data.frame (id=1:132)

countryset$METRO_ID <- c('Vienna', 'Graz', 'Linz', 'Brussels', 'Antwerp', 'Ghent', 'Liege', 'Berlin', 'Hamburg', 'Munich', 'Cologne', 'Frankfurt', 'Essen', 'Stuttgart', 'Leipzig', 'Dresden', 'Dortmund', 'Dusseldorf', 'Bremen', 'Hanover', 'Bochum', 'Freiburg', 'Augsburg', 'Bonn', 'Karlsruhe', 'Duisburg', 'Mannheim', 'Aachen', 'Copenhagen', 'Tallinn', 'Madrid', 'Barcelona', 'Valencia', 'Seville', 'Zaragoza', 'Malaga', 'Palmas', 'Bilbao', 'Helsinki', 'Paris', 'Lyon', 'Toulouse', 'Strasbourg', 'Bordeaux', 'Nantes', 'Lille', 'Montpellier', 'Rennes', 'Grenoble', 'Toulon', 'Marseille', 'Nice', 'Rouen', 'Rome', 'Naples', 'Turin', 'Palermo', 'Genova', 'Florence', 'Bologna', 'Catania', 'Venice', 'Mito', 'Tokyo', 'Kofu', 'Nagoya', 'Numazu', 'Osaka', 'Okayama', 'Kurashiki', 'Fukuyama', 'Hiroshima', 'Takamatsu', 'Monterrey', 'Irapuato', 'Hague', 'Amsterdam', 'Rotterdam', 'Utrecht', 'Oslo', 'Lisbon', 'Porto', 'Stockholm', 'Gothenburg', 'Malmo', 'Seattle', 'Portland', 'Minneapolis', 'Milwaukee', 'Madison', 'Buffalo', 'Albany', 'Detroit', 'Boston', 'Chicago', 'Providence', 'Toledo', 'Cleveland', 'Omaha', 'Akron', 'Pittsburgh', 'Harrisburg', 'Philadelphia', 'Columbus', 'Denver', 'Indianapolis', 'Dayton', 'Baltimore', 'Cincinnati', 'Washington', 'Louisville',  'Wichita', 'Richmond', 'Fresno', 'Nashville', 'Tulsa', 'Raleigh', 'Charlotte', 'Albuquerque', 'Memphis', 'Columbia', 'Atlanta', 'Phoenix',  'Dallas', 'Charleston', 'Tucson', 'Austin', 'Jacksonville', 'Houston', 'Orlando', 'Tampa', 'Miami')
countryset$id <- NULL

countryset$Country <- c('Austria', 'Austria', 'Austria', 'Belgium', 'Belgium', 'Belgium', 'Belgium', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Germany', 'Denmark', 'Estonia', 'Spain', 'Spain', 'Spain', 'Spain', 'Spain', 'Spain', 'Spain', 'Spain', 'Finland', 'France', 'France', 'France', 'France', 'France', 'France', 'France', 'France', 'France', 'France', 'France', 'France', 'France', 'France', 'Italy', 'Italy', 'Italy', 'Italy', 'Italy', 'Italy', 'Italy', 'Italy', 'Italy', 'Japan', 'Japan', 'Japan', 'Japan', 'Japan', 'Japan', 'Japan', 'Japan', 'Japan', 'Japan', 'Japan', 'Mexico', 'Mexico', 'Netherlands', 'Netherlands', 'Netherlands', 'Netherlands', 'Norway', 'Portugal', 'Portugal', 'Sweden', 'Sweden', 'Sweden', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States',  'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States',  'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States', 'United States')

datasetscat <- merge(dataset , countryset , by=c("METRO_ID")) 


n2 <- nPlot(Patents ~ hifol, data = datasetscat, type = "scatterChart", 
    group = "Country")
n2$xAxis(axisLabel = "GitHub Follower Counts")  # add x axis label
n2$yAxis(axisLabel = "Patent Counts")
n2$print("nvd3Scatter", cdn = FALSE, include_assets = TRUE)
```
